How fluid-mechanical erosion creates anisotropic porous media

### 2022-06-17 docs/PhysicsPaper/StokesErosion.tex
Added figures
NM

\vsp{5}

Figure \ref{FigVortVel} shows an example illustration of 80 eroding bodies

@@

%^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
\begin{figure*}[] \centering
        \subfigure[ Vorticity field]{ \label{FigVort}
            \includegraphics[width=0.9 \textwidth]{figs/80circ8vort.pdf} } \\
        \subfigure[ Velocity magnitude]{ \label{FigVel}
            \includegraphics[width=0.9 \textwidth]{figs/80circ8vel.pdf} }
   \caption{80 eroding bodies}
   \label{FigVortVel}
\end{figure*}
%^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
% Data from 80circ8

\begin{comment}
%^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
\begin{figure*}%[htbp]
\centering \label{fig1}
\includegraphics[width = 0.9 \textwidth]{./figs/80circ8vel.pdf}
\caption{caption}
\end{figure*}
 %^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
\end{comment}

@@

%---------------------------------------------------------%
\begin{figure*}%[htbp]
\centering \label{fig2}
\includegraphics[width = 0.99 \textwidth]{./figs/fig2.pdf}
\caption{A single simulation of porous-medium erosion. The initial configuration consists of 100 circular bodies of random size and position, as seen in Fig.~1? a) As the medium erodes, the fraction of solid-body area decreases, or, equivalently, the porosity increases. b) Resistance to flow can be characterized by either the inverse permeability, $1/k$, or the cumulative drag, the two of which are related through \eqref{ResistDrag}. Both are seen to decrease as the medium erodes, and relationship \eqref{ResistDrag} is confirmed by the simulation data.
c) The relationship between permeability $k$ and porosity $\phi$ for the eroding medium. Both quantities increase with time as the medium erodes, but at different rates due to changes in the microstructure and channelization of the medium.
}
\end{figure*}
%---------------------------------------------------------%
% Data from 100-3

%---------------------------------------------------------%
\begin{figure*}%[htbp]
\centering \label{fig3}
\includegraphics[width = 0.99 \textwidth]{./figs/fig3.pdf}
\caption{
Permeability
}
\end{figure*}
%---------------------------------------------------------%
% Data from 100-3

>>>>

	Figure \ref{fig1} shows an example simulation of the erosion of 80 bodies, with the local speed of the intervening fluid flow shown by color. This simulation illustrates the {\em channelization} process, in which regions of high flow speed create higher local shear rates, thus preferentially removing solid material, and further opening the channels. The positive feedback creates the channels that are clearly visible by in final two images.

%\ref{fig1}

%^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
\begin{figure*}%[htbp]
\centering \label{fig1}
\includegraphics[width = 0.99 \textwidth]{./figs/Velocity-80-4.pdf}
\caption{Numerical simulation of a dense suspension of 80 bodies eroding in a Stokes flow.
Over time, the non-uniform erosion of material opens channels in the medium, leading to high anisotropy.}
\end{figure*}
 %^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%

@@

@@

%---------------------------------------------------------%
\begin{figure*}%[htbp]
\centering \label{fig2}
\includegraphics[width = 0.99 \textwidth]{./figs/fig2.pdf}
\caption{A single simulation of porous-medium erosion. The initial configuration consists of XX circular bodies of random size and position, as seen in Fig.~1? a) As the medium erodes, the fraction of solid-body area decreases, or, equivalently, the porosity increases. b) Resistance to flow can be characterized by either the inverse permeability, $1/k$, or the cumulative drag, the two of which are related through \eqref{ResistDrag}. Both are seen to decrease as the medium erodes, and relationship \eqref{ResistDrag} is confirmed by the simulation data.
c) The relationship between permeability $k$ and porosity $\phi$ for the eroding medium. Both quantities increase with time as the medium erodes, but at different rates due to changes in the microstructure and channelization of the medium.
}
\end{figure*}
%---------------------------------------------------------%

%---------------------------------------------------------%
\begin{figure*}%[htbp]
\centering \label{fig3}
\includegraphics[width = 0.99 \textwidth]{./figs/fig3.pdf}
\caption{
Permeability
}
\end{figure*}
%---------------------------------------------------------%
